---
title: "Appendix: R Code for 2017 Rice Subsidy Analysis"
author: "Jannisah M. Palo"
format: pdf
editor: source
warning: false
---

# Appendix: R Code

## A.1 Data Loading

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(readr)
library(dplyr)
library(ggplot2)
library(broom)
library(scales)
library(EValue)

# Load all survey years
hh11     <- suppressMessages(read_csv("APIS PUF 2011 Household.CSV"))
person11 <- read_csv("APIS PUF 2011 Person.CSV")

hh13     <- read_csv("APIS PUF 2013 Household.CSV")
person13 <- read_csv("APIS PUF 2013 Person.CSV")

hh14     <- read_csv("APIS PUF 2014 Household.CSV")
person14 <- read_csv("APIS PUF 2014 Person.CSV")

hh16     <- read_csv("APIS PUF 2016 Household.CSV")
person16 <- read_csv("APIS PUF 2016 Person.CSV")

hh17     <- read_csv("APIS PUF 2017 Household.CSV")
person17 <- read_csv("APIS PUF 2017 Person.CSV")
```

---

## A.2 Household-Level Dataset Construction

```{r}
# 2011
person11_hh <- person11 %>%
  rename(ID = PHHNUM, PPS01 = PPS04) %>%
  group_by(ID) %>%
  summarise(fourps = as.integer(any(PPS01 == 1, na.rm = TRUE)), .groups = "drop")

hh_2011 <- hh11 %>%
  rename(ID = PHHNUM) %>%
  left_join(person11_hh, by = "ID") %>%
  mutate(fourps = ifelse(is.na(fourps), 0, fourps), year = 2011) %>%
  rename(REGN = PREG, FSIZE = PUFSIZE, RFACT = HHWGT,
         PUFEQ5 = PUFFQ5, PUFEQ6G = PUFFQ6G,
         FOOD = PUFFOOD, TOINC = PUFTOTINC,
         PUFH12_HGC = PUFH14_HGC) %>%
  filter(REGN == 10)

# 2013
person13_hh <- person13 %>%
  rename(ID = SEQ) %>%
  group_by(ID) %>%
  summarise(fourps = as.integer(any(PPS01 == 1, na.rm = TRUE)), .groups = "drop")

hh_2013 <- hh13 %>%
  rename(ID = SEQ) %>%
  left_join(person13_hh, by = "ID") %>%
  mutate(fourps = ifelse(is.na(fourps), 0, fourps), year = 2013) %>%
  rename(REGN = REGION, FOOD = T_FOOD, PUFH12_HGC = PUFH14_HGC) %>%
  filter(REGN == 10)

# 2014
person14_hh <- person14 %>%
  group_by(ID) %>%
  summarise(fourps = as.integer(any(PPS01 == 1, na.rm = TRUE)), .groups = "drop")

hh_2014 <- hh14 %>%
  left_join(person14_hh, by = "ID") %>%
  mutate(fourps = ifelse(is.na(fourps), 0, fourps), year = 2014) %>%
  rename(PUFEQ6G = PUFFQ6G, PUFEQ5 = PUFFQ5) %>%
  filter(REGN == 10)

# 2016
person16_hh <- person16 %>%
  group_by(ID) %>%
  summarise(fourps = as.integer(any(PPS01 == 1, na.rm = TRUE)), .groups = "drop")

hh_2016 <- hh16 %>%
  left_join(person16_hh, by = "ID") %>%
  mutate(fourps = ifelse(is.na(fourps), 0, fourps), post = 0, year = 2016) %>%
  filter(REGN == 10)

# 2017
person17_hh <- person17 %>%
  group_by(ID) %>%
  summarise(fourps = as.integer(any(PPS01 == 1, na.rm = TRUE)), .groups = "drop")

hh_2017 <- hh17 %>%
  left_join(person17_hh, by = "ID") %>%
  mutate(fourps = ifelse(is.na(fourps), 0, fourps), post = 1, year = 2017) %>%
  rename(REGN = REGO) %>%
  filter(REGN == 10)
```

---

## A.3 Stacking and Variable Preparation

```{r}
# Coerce all to character before stacking
hh_2011 <- hh_2011 %>% mutate(across(everything(), as.character))
hh_2013 <- hh_2013 %>% mutate(across(everything(), as.character))
hh_2014 <- hh_2014 %>% mutate(across(everything(), as.character))
hh_2016 <- hh_2016 %>% mutate(across(everything(), as.character))
hh_2017 <- hh_2017 %>% mutate(across(everything(), as.character))

# Five-year panel (for pre-trend and event study)
combined5 <- bind_rows(hh_2011, hh_2013, hh_2014, hh_2016, hh_2017) %>%
  filter(REGN == 10)

with(combined5, table(fourps, post))
```

```{r}
# Convert all analysis variables to numeric
combined5 <- combined5 %>%
  mutate(
    fourps     = as.numeric(fourps),
    post       = as.numeric(post),
    FOOD       = as.numeric(FOOD),
    year       = as.numeric(year),
    REGN       = as.factor(REGN),
    RFACT      = as.numeric(RFACT),
    FSIZE      = as.numeric(FSIZE),
    PUFEQ5     = as.numeric(PUFEQ5),
    PUFEQ6G    = as.numeric(PUFEQ6G),
    TOINC      = as.numeric(TOINC),
    PUFH04_SEX = as.numeric(PUFH04_SEX),
    PUFH05_AGE = as.numeric(PUFH05_AGE)
  )

# Two-year DiD dataset (2016–2017, complete cases only)
did_data <- combined5 %>%
  filter(year %in% c(2016, 2017)) %>%
  filter(!is.na(FOOD), !is.na(fourps), !is.na(post), !is.na(year),
         !is.na(REGN), !is.na(RFACT), !is.na(FSIZE),
         !is.na(PUFEQ5), !is.na(PUFEQ6G), !is.na(TOINC),
         !is.na(PUFH04_SEX), !is.na(PUFH05_AGE))

with(did_data, table(fourps, post))
```

---

## A.4 Difference-in-Differences Models

### Basic DiD

```{r}
did_model <- lm(FOOD ~ fourps * post, data = did_data)
summary(did_model)
```

### DiD with Covariates and Survey Weights (Final Model)

```{r}
did_model_w <- lm(
  FOOD ~ fourps * post + FSIZE + log(TOINC) + PUFEQ6G,
  data    = did_data,
  weights = RFACT
)
summary(did_model_w)
```

---

## A.5 DiD Plot

```{r}
# Compute weighted group means (2016–2017)
trend_dataa <- combined5 %>%
  filter(year %in% c(2016, 2017), !is.na(FOOD), !is.na(RFACT)) %>%
  group_by(year, fourps) %>%
  summarise(mean_food = weighted.mean(FOOD, w = RFACT, na.rm = TRUE),
            .groups = "drop")

# Counterfactual trend for treated group
treat_2016  <- trend_dataa %>% filter(year == 2016, fourps == 1) %>% pull(mean_food)
treat_2017  <- trend_dataa %>% filter(year == 2017, fourps == 1) %>% pull(mean_food)
control_change <- (trend_dataa %>% filter(year == 2017, fourps == 0) %>% pull(mean_food)) -
                  (trend_dataa %>% filter(year == 2016, fourps == 0) %>% pull(mean_food))
cf_2017 <- treat_2016 + control_change

counterfactual <- data.frame(year = c(2016, 2017),
                              mean_food = c(treat_2016, cf_2017))
```

```{r, echo=FALSE}
did_plot <- ggplot(trend_dataa,
       aes(x = year, y = mean_food,
           color = factor(fourps), group = factor(fourps))) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3.5, shape = 21, fill = "white", stroke = 1.5) +
  geom_line(data = counterfactual,
            aes(x = year, y = mean_food),
            linetype = "dashed", color = "black",
            linewidth = 1, inherit.aes = FALSE) +
  geom_segment(aes(x = 2017, xend = 2017,
                   y = cf_2017, yend = treat_2017),
               color = "black", linewidth = 0.8,
               arrow = arrow(ends = "both", length = unit(0.2, "cm")),
               inherit.aes = FALSE) +
  annotate("text", x = 2017.05, y = (cf_2017 + treat_2017) / 2,
           label = "DiD = \u20B12,753", hjust = 0, size = 3.5, color = "black") +
  annotate("text", x = 2016.5, y = cf_2017 - 500,
           label = "Counterfactual", hjust = 0, size = 3,
           color = "black", fontface = "italic") +
  scale_color_manual(values = c("0" = "#E07B6A", "1" = "#5B9BD5"),
                     labels = c("Non-4Ps", "4Ps")) +
  scale_x_continuous(breaks = c(2016, 2017),
                     labels = c("2016\n(Pre)", "2017\n(Post)")) +
  scale_y_continuous(labels = comma_format(prefix = "\u20B1")) +
  labs(x = "Survey Year", y = "Weighted Mean Food Expenditure (\u20B1)",
       color = "Household Group",
       title = "Difference-in-Differences: Food Expenditure Trends",
       subtitle = "4Ps and Non-4Ps Households, Region X (2016\u20132017)",
       caption = paste0("Note: Dashed line represents counterfactual trend for 4Ps households.\n",
                        "Source: APIS 2016 and 2017, Philippine Statistics Authority.")) +
  theme_classic() +
  theme(
    plot.title    = element_text(face = "bold", size = 13, hjust = 0),
    plot.subtitle = element_text(size = 10, color = "gray40", hjust = 0),
    plot.caption  = element_text(size = 8, color = "gray50", hjust = 0),
    axis.title    = element_text(size = 11, face = "bold"),
    axis.text     = element_text(size = 10),
    legend.position   = "right",
    legend.title      = element_text(face = "bold", size = 10),
    legend.text       = element_text(size = 10),
    legend.background = element_rect(fill = "white", color = "gray80"),
    panel.grid.major.y = element_line(color = "gray90", linewidth = 0.5),
    panel.grid.major.x = element_blank(),
    plot.margin = margin(15, 15, 15, 15)
  )

ggsave("did_plot.png", plot = did_plot, width = 7, height = 5, dpi = 300, bg = "white")
did_plot
```

---

## A.6 Extended DiD Plot (All Survey Years, 2011–2017)

```{r}
# Weighted group means across all five years
trend_data <- combined5 %>%
  filter(year %in% c(2011, 2013, 2014, 2016, 2017),
         !is.na(FOOD), !is.na(RFACT)) %>%
  group_by(year, fourps) %>%
  summarise(mean_food = weighted.mean(FOOD, w = RFACT, na.rm = TRUE),
            .groups = "drop")

# Counterfactual
treat_2016     <- trend_data %>% filter(year == 2016, fourps == 1) %>% pull(mean_food)
treat_2017     <- trend_data %>% filter(year == 2017, fourps == 1) %>% pull(mean_food)
control_change <- (trend_data %>% filter(year == 2017, fourps == 0) %>% pull(mean_food)) -
                  (trend_data %>% filter(year == 2016, fourps == 0) %>% pull(mean_food))
cf_2017        <- treat_2016 + control_change

counterfactual <- data.frame(year = c(2016, 2017),
                              mean_food = c(treat_2016, cf_2017))
```

```{r, echo=FALSE}
font_15 <- 15 / .pt

did_rice_plot <- ggplot(trend_data,
       aes(x = year, y = mean_food,
           color = factor(fourps), group = factor(fourps))) +
  annotate("rect", xmin = 2010.5, xmax = 2016.25, ymin = -Inf, ymax = Inf,
           fill = "gray95", alpha = 0.5) +
  annotate("rect", xmin = 2016.25, xmax = 2017.5, ymin = -Inf, ymax = Inf,
           fill = "lightyellow", alpha = 0.5) +
  geom_vline(xintercept = 2016.25, linetype = "dotted",
             color = "gray40", linewidth = 0.8) +
  annotate("text", x = 2013.5, y = 38500, label = "Pre-Intervention",
           size = font_15, color = "gray40", fontface = "italic") +
  annotate("text", x = 2017, y = 38500, label = "Post",
           size = font_15, color = "gray40", fontface = "italic") +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3, shape = 21, fill = "white", stroke = 1.5) +
  geom_line(data = counterfactual, aes(x = year, y = mean_food),
            linetype = "dashed", color = "black",
            linewidth = 1, inherit.aes = FALSE) +
  geom_segment(aes(x = 2017, xend = 2017, y = cf_2017, yend = treat_2017),
               color = "black", linewidth = 0.8,
               arrow = arrow(ends = "both", length = unit(0.2, "cm")),
               inherit.aes = FALSE) +
  annotate("text", x = 2016.42, y = cf_2017 - 900,
           label = "Counterfactual", hjust = 0, size = font_15,
           color = "black", fontface = "italic") +
  scale_color_manual(values = c("0" = "#E07B6A", "1" = "#5B9BD5"),
                     labels = c("Non-4Ps", "4Ps")) +
  scale_x_continuous(breaks = c(2011, 2013, 2014, 2016, 2017),
                     limits = c(2010.5, 2018.1)) +
  scale_y_continuous(labels = comma_format(prefix = "\u20B1"),
                     limits = c(25000, 40000)) +
  coord_cartesian(clip = "off") +
  labs(x = "Survey Year", y = "Mean Food Expenditure (\u20B1)",
       color = "Household Group",
       title = "Food Expenditure Trends of 4Ps and Non-4Ps Households",
       subtitle = "Region X, APIS 2011\u20132017 | Dashed line = counterfactual trend") +
  theme_classic(base_size = 15) +
  theme(
    plot.title    = element_text(face = "bold", size = 15, hjust = 0),
    plot.subtitle = element_text(size = 15, color = "gray40", hjust = 0),
    axis.title    = element_text(size = 15, face = "bold"),
    axis.text     = element_text(size = 15),
    legend.position   = "right",
    legend.title      = element_text(face = "bold", size = 15),
    legend.text       = element_text(size = 15),
    legend.background = element_rect(fill = "white", color = "gray80"),
    panel.grid.major.y = element_line(color = "gray90", linewidth = 0.4),
    panel.grid.major.x = element_blank(),
    plot.margin = margin(15, 40, 15, 15)
  )

ggsave("did_rice_plot.png", plot = did_rice_plot,
       width = 9, height = 5, dpi = 300, bg = "white")
did_rice_plot
```

---

## A.7 Parallel Trends Assumption Tests

### A.7.1 Pre-Treatment Trends Plot (2011–2016)

```{r, echo=FALSE}
trend_pre <- combined5 %>%
  filter(year %in% c(2011, 2013, 2014, 2016), !is.na(FOOD), !is.na(RFACT)) %>%
  group_by(year, fourps) %>%
  summarise(mean_food = weighted.mean(FOOD, w = RFACT, na.rm = TRUE),
            .groups = "drop")

pre_did_plot <- ggplot(trend_pre,
       aes(x = year, y = mean_food,
           color = factor(fourps), group = factor(fourps))) +
  annotate("rect", xmin = 2010.5, xmax = 2016.5, ymin = -Inf, ymax = Inf,
           fill = "gray95", alpha = 0.5) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3.5, shape = 21, fill = "white", stroke = 1.5) +
  geom_text(aes(label = paste0("\u20B1", format(round(mean_food, 0), big.mark = ","))),
            vjust = -1.2, size = 2.8, show.legend = FALSE) +
  scale_color_manual(values = c("0" = "#E07B6A", "1" = "#5B9BD5"),
                     labels = c("Non-4Ps (Control)", "4Ps (Treated)")) +
  scale_x_continuous(breaks = c(2011, 2013, 2014, 2016)) +
  scale_y_continuous(labels = comma_format(prefix = "\u20B1"),
                     limits = c(25000, 40000)) +
  labs(x = "Survey Year", y = "Mean Food Expenditure (\u20B1)",
       color = "Household Group",
       title = "Pre-Treatment Trends",
       subtitle = "Region X | APIS 2011\u20132016") +
  theme_classic(base_size = 15) +
  theme(
    plot.title    = element_text(face = "bold", size = 15, hjust = 0),
    plot.subtitle = element_text(size = 15, color = "gray40", hjust = 0),
    axis.title    = element_text(size = 15, face = "bold"),
    axis.text     = element_text(size = 15),
    legend.position   = "right",
    legend.title      = element_text(face = "bold", size = 15),
    legend.text       = element_text(size = 15),
    legend.background = element_rect(fill = "white", color = "gray80"),
    panel.grid.major.y = element_line(color = "gray90", linewidth = 0.4),
    panel.grid.major.x = element_blank(),
    plot.margin = margin(15, 20, 15, 15)
  )

ggsave("pre_did_rice_plot.png", plot = pre_did_plot,
       width = 8, height = 5, dpi = 300, bg = "white")
pre_did_plot
```

### A.7.2 Placebo DiD Test (2014 vs. 2016)

```{r}
# Assign fake post indicator: treat 2016 as "post" under a placebo policy in 2014
placebo_data <- combined5 %>%
  filter(year %in% c(2014, 2016)) %>%
  mutate(post = ifelse(year == 2016, 1, 0)) %>%
  filter(!is.na(FOOD), !is.na(fourps), !is.na(RFACT),
         !is.na(FSIZE), !is.na(PUFEQ6G), !is.na(TOINC),
         !is.na(PUFH04_SEX), !is.na(PUFH05_AGE))

did_placebo <- lm(
  FOOD ~ fourps * post + FSIZE + log(TOINC) + PUFEQ6G,
  data    = placebo_data,
  weights = RFACT
)
summary(did_placebo)
```

---

## A.8 Event Study

```{r}
# All five survey years; 2016 as reference year
combined_es <- combined5 %>%
  filter(year %in% c(2011, 2013, 2014, 2016, 2017)) %>%
  mutate(year = relevel(factor(year), ref = "2016"))

event_model <- lm(
  FOOD ~ fourps * year + FSIZE + log(TOINC) + PUFEQ6G,
  data    = combined_es,
  weights = RFACT
)
summary(event_model)
```

```{r, echo=FALSE}
# Extract and prepare interaction coefficients
event_results <- tidy(event_model) %>%
  filter(grepl("fourps:year", term)) %>%
  mutate(
    year    = c(2011, 2013, 2014, 2017),
    period  = ifelse(year == 2017, "Post-Intervention", "Pre-Intervention"),
    ci_low  = estimate - 1.645 * std.error,
    ci_high = estimate + 1.645 * std.error,
    significant = ifelse(ci_low > 0 | ci_high < 0, "Significant", "Not Significant")
  )

font_15 <- 15 / .pt

event_study_plot <- ggplot(event_results, aes(x = year, y = estimate)) +
  annotate("rect", xmin = 2010.5, xmax = 2016.25, ymin = -Inf, ymax = Inf,
           fill = "gray95", alpha = 0.6) +
  annotate("rect", xmin = 2016.25, xmax = 2017.5, ymin = -Inf, ymax = Inf,
           fill = "lightyellow", alpha = 0.6) +
  geom_vline(xintercept = 2016.25, linetype = "dotted",
             color = "gray40", linewidth = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed",
             color = "gray30", linewidth = 0.8) +
  annotate("text", x = 2013, y = max(event_results$ci_high) * 0.97,
           label = "Pre-Intervention", size = font_15,
           color = "gray40", fontface = "italic") +
  annotate("text", x = 2016.6, y = max(event_results$ci_high) * 0.97,
           label = "Post", size = font_15,
           color = "gray40", fontface = "italic") +
  annotate("text", x = 2015.8, y = min(event_results$ci_low) * 0.85,
           label = "Reference\nYear (2016)", size = font_15,
           color = "gray50", fontface = "italic") +
  annotate("point", x = 2016, y = 0, size = 3, shape = 21,
           fill = "white", color = "gray50", stroke = 1.2) +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high, color = significant),
                width = 0.3, linewidth = 0.9) +
  geom_point(aes(color = significant, fill = significant),
             size = 2.8, shape = 21, stroke = 1.5) +
  scale_color_manual(values = c("Significant" = "#E07B6A",
                                "Not Significant" = "#5B9BD5")) +
  scale_fill_manual(values  = c("Significant" = "#E07B6A",
                                "Not Significant" = "#5B9BD5")) +
  scale_x_continuous(breaks = c(2011, 2013, 2014, 2016, 2017),
                     labels = c("2011", "2013", "2014",
                                "2016\n(Ref)", "2017\n(Post)")) +
  scale_y_continuous(labels = comma_format(prefix = "\u20B1")) +
  labs(x = "Survey Year",
       y = "Treatment Effect on Food Expenditure (\u20B1)",
       color = "Statistical Significance",
       fill  = "Statistical Significance",
       title = "Event Study: Effect of Rice Subsidy on Food Expenditure",
       subtitle = "Region X | Reference year: 2016 | 90% confidence intervals shown") +
  theme_classic(base_size = 15) +
  theme(
    plot.title    = element_text(face = "bold", size = 15, hjust = 0),
    plot.subtitle = element_text(size = 15, color = "gray40", hjust = 0),
    axis.title    = element_text(size = 15, face = "bold"),
    axis.text     = element_text(size = 15),
    legend.position    = "none",
    panel.grid.major.y = element_line(color = "gray90", linewidth = 0.4),
    panel.grid.major.x = element_blank(),
    plot.margin = margin(15, 20, 15, 15)
  )

ggsave("event_study_did_rice_plot.png", plot = event_study_plot,
       width = 8, height = 5, dpi = 300, bg = "white")
event_study_plot
```


# =============================================================================
# E-VALUE SENSITIVITY ANALYSIS FOR DiD
# =============================================================================

## E-Value Input Parameters

```{r}
est  <- coef(did_model_w)["fourps:post"]
print(est)
se <- coef(summary(did_model_w))["fourps:post", "Std. Error"]
print(se)
sd_y <- sigma(did_model_w)
print(sd_y)
```

## E-Value Results

```{r}
EValue::evalues.OLS(est = est, se = se, sd = sd_y, delta = 1)
```


## E-Value Contour Plot

```{r}
# ── 1. Rice DiD model ───────────────────────────────────────────────────────
did_model_w <- lm(
  FOOD ~ fourps * post + FSIZE + log(TOINC) + PUFEQ6G,
  data    = did_data,
  weights = RFACT
)

# ── 2. Extract DiD coefficient, SE, and residual SD ──────────────────────────
est  <- coef(did_model_w)["fourps:post"]
se <- coef(summary(did_model_w))["fourps:post", "Std. Error"]
sd_y <- sigma(did_model_w)

# ── 3. Compute E-values ──────────────────────────────────────────────────────
ev_rice <- EValue::evalues.OLS(
  est   = est,
  se    = se,
  sd    = sd_y,
  delta = 1
)

# ── 4. Extract RR and E-values ───────────────────────────────────────────────
rr_point <- ev_rice["RR", "point"]
rr_lower <- ev_rice["RR", "lower"]

e_point <- ev_rice["E-values", "point"]
e_ci    <- ev_rice["E-values", "lower"]

# ── 5. E-value contour function ──────────────────────────────────────────────
evalue_curve <- function(x, rr) {
  rr * (x - 1) / (x - rr)
}

# ── 6. Curve data ────────────────────────────────────────────────────────────
# Point-estimate contour
df_point <- data.frame(
  x = seq(rr_point + 0.0001, 1.35, length.out = 2000)
)
df_point$y <- evalue_curve(df_point$x, rr_point)
df_point <- subset(df_point, y >= 1 & y <= 6)

# CI contour
df_ci <- data.frame(
  x = seq(rr_lower + 0.0001, 1.35, length.out = 2000)
)
df_ci$y <- evalue_curve(df_ci$x, rr_lower)
df_ci <- subset(df_ci, y >= 1 & y <= 6)

# ── 7. Labels ────────────────────────────────────────────────────────────────
point_label <- data.frame(
  x = e_point,
  y = e_point,
  label = sprintf("E-value: (%.3f, %.3f)", e_point, e_point)
)

ci_label <- data.frame(
  x = e_ci,
  y = e_ci,
  label = sprintf("E-value (CI): (%.3f, %.3f)", e_ci, e_ci)
)

# ── 8. Plot ────────────────────────────────────────────────────────────────
p_rice <- ggplot() +
  annotate("rect", xmin = 1, xmax = 6, ymin = 1,
           ymax = 6, fill = "grey80", alpha = 0.30) +
  
  geom_hline(yintercept = 1, linetype =
               "dashed", linewidth = 0.7, color = "grey50") +
  
  geom_line(data = df_point, aes(x = x, y = y),
            color = "#3266AD", linewidth = 1.3) +
  
  geom_line(data = df_ci, aes(x = x, y = y),
            color = "grey55", linewidth = 1.0, linetype = "dashed") +
  
  geom_point(data = point_label, aes(x = x,
                                     y = y), shape = 21, size = 3,
             fill = "white", color = "#3266AD", stroke = 1.6) +
  
  geom_text(data = point_label, aes(x = x, 
                                    y = y, label = label),
            nudge_x = 0.03, nudge_y = 0.03,   
            hjust = 0, size = 3.2, color = "#3266AD") +
  
  geom_point(data = ci_label, aes(x = x, y = y),
             shape = 21, size = 3,
             fill = "white", color = "grey45",
             stroke = 1.6) +
  
  geom_text(data = ci_label, aes(x = x, y = y,
                                 label = label),
            nudge_x = 0.02, nudge_y = 0.02,
            hjust = 0, size = 3.2, color = "grey35") +
  
  labs(title = "E-value Contour Plot",
       subtitle = "Rice Subsidy ATT Estimate",
       x = "Confounder–Exposure association (RR scale)",
       y = "Confounder–Outcome association (RR scale)") +
  
  coord_cartesian(
    xlim = c(0.99, 1.3),
    ylim = c(0.99, 1.3),
    clip = "on"            
  ) +
  
  scale_x_continuous(breaks = seq(1.0, 1.3, by = 0.1)) +
  scale_y_continuous(breaks = seq(1.0, 1.3, by = 0.1)) +
  
  theme_minimal(base_size = 13) +
  
  theme(
    plot.title = element_text(face = "bold",
                              size = 14, hjust = 0, color = "grey10", 
                              margin = margin(b = 4)),
    
    plot.subtitle = element_text(size = 10,
                                 hjust = 0, color = "grey45", 
                                 margin = margin(b = 10)),
    
    axis.title = element_text(face = "bold",
                              size = 11, color = "grey20"),
    
    axis.text = element_text(color = "grey30",
                             size = 10),
    
    axis.line = element_line(color = "grey30",
                             linewidth = 0.4),
    
    panel.grid.major = element_line(color = "grey88", linewidth = 0.35),
    panel.grid.minor = element_blank(),
    plot.margin = margin(15, 25, 15, 15)
  )

p_rice

ggsave("evalue_did_rice_plot.png", plot = p_rice, 
       width = 7, height = 4.5, dpi = 300, bg = "white")
```




